Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-27 papers/thesis-kirstie/thesis.tex
add equation numbers

The liquid ideal Helmholtz free energy $F_{Hideal}$ is computed 
analytically for a given homogeneous reduced density $n^*$, and reduced 
temperature $t^*$ from the equation 
%\begin{displaymath}{\frac{F_{Hideal}}{V}=k_BTn(\ln(\frac{n*2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)-DELETE-EQN!}\end{displaymath} 
\begin{displaymath}{\frac{F_{Hideal}}{V}=k_BTn(\ln(n\Lambda^3)-1.0)}\end{displaymath} 
where $\sigma=1$ (which gives $n^*=n\sigma^3$=n), and $\epsilon=1$ (which 
gives $t^*=\frac{k_BT}{\epsilon}=k_BT$). The quantity $\Lambda$ is the DeBroglie 
wavelength given by
\begin{displaymath}{\Lambda =\sqrt{\frac{2\pi\hbar^2}{k_BTm}}}\end{displaymath}  
where in our program we have set
\begin{displaymath}\left(\sqrt{\frac{2\hbar^2}{m}}\right)^3=4.752731840013864\text{x}10^{-7}\color{red}units?\color{black}\end{displaymath} 
%\begin{displaymath}{m=}\end{displaymath}  
%\begin{displaymath}{\hbar=}\end{displaymath} 
%\begin{displaymath}{k_B=}\end{displaymath}

The crystal ideal Helmholtz free energy $F_{Cideal}$ is computed from the equation 
\begin{displaymath}{F_{Cideal}[n(\vec{r})]= k_BT\int[n(\vec{r})\ln(n(\vec{r})\Lambda^3)-n(\vec{r})]dV}\end{displaymath}
with the varying number density profile given by 
\begin{displaymath}
  {n(|\vec{r}-\vec{R_i}|)=\sum_i{(1-f_v)\frac{\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}}
\end{displaymath}
For small gw values it is assumed that the Guassians do not overlap, 
in which case the equation for the free energy can be simplified, and solved
analytically with the result
\begin{equation}
 F_{Cideal}=(1-f_v)k_BT\left(\ln((1-f_v)\Lambda^3)-3\ln(\sqrt{2\pi{gw}})-\frac{5.0}{2}\right)
\end{equation}
For larger gw values it is assumed that the Gaussians do overlap, 
and so the free energy is caluculated computationally. First dx is scaled by gw,
\begin{equation}
  dx_{scaled} = (dx_{input})(gw)
\end{equation}
and then $n(\vec{r})$ is computed at one position of $\vec{r}$ within the 
primitive cell taking into account the contribution of Gaussians from 
many (5x5x5) nearby cells whose centers are given by $R_i$.
%\begin{displaymath}{n(|\vec{r}-\vec{R_i}|)+=\frac{(1-f_v)\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}\end{displaymath}
The contribution to the free energy of $n(\vec{r})$ at the one position is then
added to the accumulating sum.
%\begin{displaymath}{cF_{ideal}+=k_BTn(ln(\frac{(n)2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)dV-DELETE-EQN!}\end{displaymath}
%\begin{displaymath}{cF_{ideal}+=k_BTn(\ln(n\Lambda^3)-1.0)dV}\end{displaymath}
This process is repeated for all positions within one primitive cell to get the
crystal ideal free energy for the primitive cell. This energy is then divided by
the volume of the primitive cell to get the crystal ideal free energy per
volume.

>>>>

The liquid ideal Helmholtz free energy $F_{Hideal}$ is computed 
analytically for a given homogeneous reduced density $n^*$, and reduced 
temperature $t^*$ from the equation 
%\begin{displaymath}{\frac{F_{Hideal}}{V}=k_BTn(\ln(\frac{n*2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)-DELETE-EQN!}\end{displaymath} 
\begin{align}
  \frac{F_{Hideal}}{V}=k_BTn(\ln(n\Lambda^3)-1.0)
\end{align}
where $\sigma=1$ (which gives $n^*=n\sigma^3$=n), and $\epsilon=1$ (which 
gives $t^*=\frac{k_BT}{\epsilon}=k_BT$). The quantity $\Lambda$ is the DeBroglie 
wavelength given by
\begin{displaymath}{\Lambda =\sqrt{\frac{2\pi\hbar^2}{k_BTm}}}\end{displaymath}  
where in our program we have set
\begin{displaymath}\left(\sqrt{\frac{2\hbar^2}{m}}\right)^3=4.752731840013864\text{x}10^{-7}\color{red}units?\color{black}\end{displaymath} 
%\begin{displaymath}{m=}\end{displaymath}  
%\begin{displaymath}{\hbar=}\end{displaymath} 
%\begin{displaymath}{k_B=}\end{displaymath}

The crystal ideal Helmholtz free energy $F_{Cideal}$ is computed from the equation 
\begin{align}
  F_{Cideal}[n(\vec{r})]= k_BT\int[n(\vec{r})\ln(n(\vec{r})\Lambda^3)-n(\vec{r})]dV
\end{align}
with the varying number density profile given by 
\begin{displaymath}
  {n(|\vec{r}-\vec{R_i}|)=\sum_i{(1-f_v)\frac{\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}}
\end{displaymath}
For small gw values it is assumed that the Guassians do not overlap, 
in which case the equation for the free energy can be simplified, and solved
analytically with the result
\begin{equation}
 F_{Cideal}=(1-f_v)k_BT\left(\ln((1-f_v)\Lambda^3)-3\ln(\sqrt{2\pi{gw}})-\frac{5.0}{2}\right)
\end{equation}
For larger gw values it is assumed that the Gaussians do overlap, 
and so the free energy is caluculated computationally. First dx is scaled by gw,
\begin{equation}
  dx_{scaled} = (dx_{input})(gw)
\end{equation}
and then $n(\vec{r})$ is computed at one position of $\vec{r}$ within the 
primitive cell taking into account the contribution of Gaussians from 
many (5x5x5) nearby cells whose centers are given by $R_i$.
%\begin{displaymath}{n(|\vec{r}-\vec{R_i}|)+=\frac{(1-f_v)\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}\end{displaymath}
The contribution to the free energy of $n(\vec{r})$ at the one position is then
added to the accumulating sum.
%\begin{displaymath}{cF_{ideal}+=k_BTn(ln(\frac{(n)2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)dV-DELETE-EQN!}\end{displaymath}
%\begin{displaymath}{cF_{ideal}+=k_BTn(\ln(n\Lambda^3)-1.0)dV}\end{displaymath}
This process is repeated for all positions within one primitive cell to get the
crystal ideal free energy for the primitive cell. This energy is then divided by
the volume of the primitive cell to get the crystal ideal free energy per
volume.
